Constraining Quiescent Supermassive Black Hole Environments.

### 2014-08-12 ms.tex
Schematic depiction of the effective wind velocity.

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}
\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}
\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\ff}{\rm ff}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}
\newcommand{\vwO}{v_{w,0}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\pyear}{{\rm yr}^{-1}}

@@

\begin{align}
&\kew n =A \phirs -B \frac{G \Mbh}{\rs}\\
&A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} \label{eq:stag_analytic}
\end{align}

@@

\begin{align}
\kew=\frac{7}{4}\frac{G \Mbh}{n \rs}
\label{eq:stag_simple}
\end{align}

@@

\begin{align}
\rs=\frac{7}{2}\frac{G \Mbh}{\vw^2}.
\label{eq:rs_simple}
\end{align}

@@

Thus, $\cs(rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to $\Mdotb$

@@

...

%%AG-Plot comparing stagnation radius and Ia radius for all profiles...I found this to be confusing/hard to explain.
%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...

>>>>

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}
\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}
\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\ff}{\rm ff}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}
\newcommand{\vwO}{v_{w,0}}
\newcommand{\kewO}{\frac{\vwO^2}{2}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\pyear}{{\rm yr}^{-1}}

@@

\begin{align}
&\kewO n =A \phirs -B \frac{G \Mbh}{\rs}\\
&A=\left[\frac{4\gamma-(\gamma-1)(1+\Gamma)}{4(\gamma-1)}\right]; \hspace{1cm} B=\frac{2-\Gamma}{4} \label{eq:stag_analytic}
\end{align}

@@

\begin{align}
\kewO=\frac{7}{4}\frac{G \Mbh}{n \rs}
\label{eq:stag_simple}
\end{align}

@@

\begin{align}
\rs=\frac{7}{2}\frac{G \Mbh}{\vwO^2}.
\label{eq:rs_simple}
\end{align}

@@

Thus, $\cs(\rs)\simeq \vw(\rs)$. This means that $\dot{M}$ in our model is quite close to $\Mdotb$

@@

The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant. For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.  Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating. Thus, for $\Mbh=10^6 \MSun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds. On the other hand, for $\Mbh \gsim 10^8 \MSun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe. These two regimes are illustrated in Figure~\ref{fig:vw_eff}.

\begin{figure}
\includegraphics[width=\columnwidth]{vw_eff.eps}
\caption{\label{fig:vw_eff} Top panel: $\vwO$ vs. $\Mbh/\Msun$ assuming $\vwO$=100 km/s (from main sequence winds) for $\rs/\rIa<1$ and $\vwO$=500 km/s (from type Ia SNes) for $\rs/\rIa>1$. Bottom panel: $\rs/\rIa$ vs. $\Mbh/\Msun$ using heating prescription above.}
\end{figure}

%AG-I am not comfortable saying type Ia SNe's don't contribute to heating for smaller mass BHs. If the cooling time for the SNe is long then it would be wrong to ignore the SNe contribution. The difference would be that the SNe heating would just be less steady.
%AG-Thornton and http://arxiv.org/pdf/1402.6695v2.pdf...
